The globular cluster system of the Auriga simulations

### 2019-10-28 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{General comments about style}
\begin{itemize}
\item
\item
\item
\item
\item I replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, I changed `Sec.' to `section' to refer to a section in one of the references.
\end{itemize}

\section*{Major comments and concerns}
\begin{itemize}
\item Item
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
\item Item
\end{itemize}

\section*{Comments for each section}
\begin{itemize}
\item Item
\end{itemize}

\section*{Minor comments}
\begin{itemize}
\item Item
\end{itemize}

\end{document}

### 2019-10-28 AurigaGCS.tex
Submitted.
Process feedback referee / General comments about style / MNRAS style to refer to...

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
methods: numerical -- galaxies: formation -- galaxies: star clusters: general.
\end{keywords}

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or M31 GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Sec.~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GCSs, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

@@

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Sec.~\ref{sec:milkyway},
and of the M31 GCS in Sec.~\ref{sec:andromeda}

@@

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}}
$r_{\text{vir,M31}} = 299$~kpc and multiply by $r_{\text{vir,MW}} = 261$~kpc to 
account for the different intrinsic sizes of both galaxies. Values for 
R$_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), but the galactocentric radius of GCs
in M31 is not available in CR16. Therefore, we follow \citet[][Sec.~4.1]{2019arXiv190111229W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs. second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue)
        [red] crosses show the values calculated using all (only {\it in~situ})
        [only accreted] GC candidates. Green triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

@@

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS)
on Astrophysics. TLRH thanks the Max Planck Computing and Data Facility for
maintaining the Freya compute cluster, where the simulations were post-processed.
FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR.
This work has been supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the SuperMUC system 
at the Leibniz Computing Centre, Garching, under the project PR85JE of the Gauss 
Centre for Supercomputing. This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology on behalf of
the STFC DiRAC HPC Facility `www.dirac.ac.uk'. This equipment was funded by BIS 
National E-infrastructure capital grant ST/K00042X/1, STFC capital grant 
ST/H008519/1 and STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.

>>>>

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
galaxies: formation -- galaxies: star clusters: general.
\end{keywords}

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or M31 GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GCSs, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

@@

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Section~\ref{sec:milkyway},
and of the M31 GCS in Section~\ref{sec:andromeda}

@@

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}}
$r_{\text{vir,M31}} = 299$~kpc and multiply by $r_{\text{vir,MW}} = 261$~kpc to 
account for the different intrinsic sizes of both galaxies. Values for 
R$_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), but the galactocentric radius of GCs
in M31 is not available in CR16. Therefore, we follow \citet[][section~4.1]{2019arXiv190111229W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs. second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue)
        [red] crosses show the values calculated using all (only {\it in~situ})
        [only accreted] GC candidates. Green triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][page~38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

@@

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS)
on Astrophysics. TLRH thanks the Max Planck Computing and Data Facility for
maintaining the Freya compute cluster, where the simulations were post-processed.
FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR. FAG 
acknowledges financial support from CONICYT through the project FONDECYT Regular 
Nr. 1181264, and funding from the Max Planck Society through a Partner Group grant.
This work has been supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the SuperMUC system 
at the Leibniz Computing Centre, Garching, under the project PR85JE of the Gauss 
Centre for Supercomputing. This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology on behalf of
the STFC DiRAC HPC Facility `www.dirac.ac.uk'. This equipment was funded by BIS 
National E-infrastructure capital grant ST/K00042X/1, STFC capital grant 
ST/H008519/1 and STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.
